---
title: "my-vignette"
author: "Lorenzo Carretero"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"my-vignette"}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Load required libraries...
```{r setup_1, echo=FALSE, warnings = FALSE, message = FALSE}
#install.packages('readr')
library(readr)
# install.packages('dplyr')
library(dplyr)
# install.packages('tidyr')
library(tidyr)
# install.packages('magrittr')
library(magrittr)
# install.packages('graphics')
library(graphics)
# install.packages('maps')
library(maps)
```

The package includes the FARS dataset files from years 2013 to 2015. To access the raw data files the user can use the following line of code:

```{r setup_2, eval=FALSE}
system.file("extdata", "accident_2013.csv.bz2", package = "BuilidinganRPackageLCP")
system.file("extdata", "accident_2014.csv.bz2", package = "BuilidinganRPackageLCP")
system.file("extdata", "accident_2015.csv.bz2", package = "BuilidinganRPackageLCP")
```


# Description

This is the vignette for the R package BuilidinganRPackageLCP written in R Markdown as a html_vignette document.  The R package BuilidinganRPackageLCP implements five useful functions to process and analyze data from the **Fatality Analysis Reporting System (FARS)**. The functions are the following:

1. *fars_read*: A read data file function.
2. *make_filename*: A simple function to create the filename of accident data for a given year.
3. *fars_read_years*: A function to extraxct monthly data from a given set of years.
4. *fars_summarize_years*: A function to summarize FARS events per month and year.
5. *fars_map_state*: A function to create a map of FARS events and points plota for a given a state number and year.


# Installation

From **CRAN**
```{r Installation_1, eval=FALSE}
install.packages('BuilidinganRPackageLCP')
```

From **GITHUB**

```{r Installation2, eval=FALSE}
devtools::install_github("Darwinita/BuilidinganRPackageLCP")
```

**LOAD** using

```{r Installation3}
library(BuilidinganRPackageLCP)
```



# Usage

### Usage of fars_read
fars_read(filename)

#### Arguments
filename, Is a character string with the name of the input data file.

### Usage of make_filename
make_filename(year)

#### Arguments
year, A numeric corresponding to the user provided year.

### Usage of fars_read_years
fars_read_years(years)

#### Arguments
years, Is a numeric vector containing the series of years for which to extract monthly FARS data.

### Usage of fars_summarize_years
fars_summarize_years(years)

#### Arguments
years, Is a numeric vector containing the series of years for which to summarize FARS data.

### Usage of fars_map_state
fars_map_state(state.num, year)

#### Arguments
state.num, Is a numeric corresponding to the user provided state number.
year, A numeric corresponding to the user provided year.

# Details
The R package BuilidinganRPackageLCP has the following main goals:

* Manage FRS data file names from user provided year(s).

* Extract and summarize FARS data from user provided year(s).

* Map FARS data per state and user provided year.


# Examples

### Example 1

```{r Example1, warnings = FALSE, message = FALSE}
#Create a dataframe from data file accident_2015.csv.bz2.
filename <- system.file("extdata", "accident_2015.csv.bz2", package = "BuilidinganRPackageLCP")
dataframe2015 <- BuilidinganRPackageLCP::fars_read(filename)
class(dataframe2015)
summary(dataframe2015)
```

### Example 2

```{r Example2, warnings = FALSE, message = FALSE}
#create the filename of FARS accident data for year 2013.
BuilidinganRPackageLCP::make_filename(2013)
```

### Example 3

```{r Example3, warnings = FALSE, message = FALSE}
#Extract the monthly FARS data from years 2013, 2014 and 2015.
fars_read_years2013_2015 <- BuilidinganRPackageLCP::fars_read_years(c(2013,2014,2015))
class(fars_read_years2013_2015)
str(fars_read_years2013_2015)
```

### Example 4

```{r Example4, warnings = FALSE, message = FALSE}
#Summarize FARS data for years 2013, 2014 and 2015.
DataSummary2013_2015 <- BuilidinganRPackageLCP::fars_summarize_years(c(2013,2014,2015))
class(DataSummary2013_2015)
str(DataSummary2013_2015)
DataSummary2013_2015
```

### Example 5

```{r Example5, warnings = FALSE, message = FALSE}
#Map FARS data for state nu. 28 in 2015.
BuilidinganRPackageLCP::fars_map_state(28,2015)
```

**Figure 1**: FARS data for state number 28 in 2015.
